Assessing the Replicability of Psychological Science Through Pedagogy

### 2016-09-08 paper/paper.Rmd
Small updates to mediating table

\begin{table}[ht]
\centering
\begin{tabular}{rl|ccccccc}
  \hline
\multicolumn{2}{c}{Replicated} & \multicolumn{2}{c}{Original on Turk?} & \multicolumn{2}{c}{High fidelity?} & \multicolumn{3}{c}{Open Materials?} \\
  \hline
   &  & No & Yes & Yes & No & No & Some & Yes \\ 
  Full & 3 & 1 & 2 & 1 & 2 & 1 & 1 & 1 \\ 
  Partial & 6 & 4 & 2 & 4 & 2 & 2 & 1 & 3 \\ 
  No &  2 &  1 &  1 &  2 & 0 &  1 & 0 &  1 \\ 
  \hline
  Total & 11 & 6 & 5 & 7 & 4 & 4 & 2 & 5 \\
   \hline
\end{tabular}
\caption{\label{tab:results} Counts of instructor team replication ratings, split by mediating variables. High fidelity denotes replications judged to be above the median rating of fidelity ( >`r median(d$fidelity)` out of 7).}
\end{table}

>>>>

\begin{table}[ht]
\centering
\begin{tabular}{rl|ccccccc}
  \hline
\multicolumn{2}{c}{Support} & \multicolumn{2}{c}{Original on Turk?} & \multicolumn{2}{c}{High fidelity?} & \multicolumn{3}{c}{Open Materials?} \\
  \hline
   &  & No & Yes & Yes & No & No & Some & Yes \\ 
  Full & 3 & 1 & 2 & 1 & 2 & 1 & 1 & 1 \\ 
  Partial & 6 & 4 & 2 & 4 & 2 & 2 & 1 & 3 \\ 
  No &  2 &  1 &  1 &  2 & 0 &  1 & 0 &  1 \\ 
  \hline
  Total & 11 & 6 & 5 & 7 & 4 & 4 & 2 & 5 \\
   \hline
\end{tabular}
\caption{\label{tab:results} Counts of instructor team ratings of replication support for the theoretical findings, split by variables of interest. High fidelity denotes replications judged to be above the median rating of fidelity ( >`r median(d$fidelity)` out of 7).}
\end{table}
